\chapter{I'm Not Okay}
\chapterauthor{bloodytearz666}

\section{Helena}

Fifteen-year-old Eternity Demen'tia Johnson warily took a seat on the Hogwarts Express. As she did so, she heard many giggles in the air. Ugh. Stupid preps. Eternity had hoped she wouldn't see any when she came to Hogwarts. They had made her life in Los Angeles High School miserable. Now she was supposed to put up with them here? She sighed sadly, and stared out of the window. In her misery, she her iPod out of her Emily the Strange bag and blared on some My Chemical Romance (\AN[\textlcsc{A/N}: ]{Don't they rock?}).

Oh great. Now even more preps were giving her dirty looks. Eternity tried her best to ignore them. t wasn't because Eternity was dirty or deformed or anything. Maybe it was something to do with her black leather corset, or her ripped black miniskirt or her black combat boots or the metal music she was listening to.

Eternity hated how people judged her like that just because she was a goth.

She was beautiful, with long raven black hair with red streaks, deathly pale ivory skin and piercing blue eyes that would make any goth man's heart beat like a subway train. She was skinny, but had curves in the right places. But her eyes still bore the sadness of the scars of her tragic past.

When she was two, Eternity's parents (she was a pureblood) had committed suicide by slitting their wrists. She was adopted when she was five, but all was not well. Her new life was hell. She was constantly abused, beat and raped by her new parents. Every night she would sit down and cry in her bed. Even at school, she was always being bullied. Her life was totally fucked-up and she couldn't stand it.

When she was eleven, she kept getting mail and stuff from Hogwarts but her adopted parents wouldn't let her go. Finally, at fourteen, she was forced to run away.

Anyway, Eternity saw someone trying to sit down next to her. She jumped to her feet. \enquote{Get the fuck out of here you fucking bastard!} she shouted. \enquote{What's wrong?} asked the person. Suddenly Eternity felt calmed down. The person had a very low, sexy voice. \enquote{Oh, I'm sorry!} Eternity apologized. \enquote{It's alright. Now can I at least fucking sit here?} asked the boy. \enquote{Fine.} said Eternity. The boy sat down. Eternity looked at his face. He was extremely hot. He had long dyed black hair and blue eyes.

\begin{sloppypar}
    \enquote{What's you're name?} asked Eternity. \enquote{Draco.} he said. \enquote{That's an unusual name. But I guess I can't fucking talk. My name's Eternity.} said Eternity. \enquote{Cool.} said Draco. Draco and Eternity shook hands. \enquote{How old are you?} Eternity wanted to know. \enquote{Fifteen. How about you?} asked Draco. \enquote{Same.} Then, the train stopped and Draco and Eternity had to separate.
\end{sloppypar}
