\section{Duality}

a/n: look, I don't care when the f Harry Potter is in my version it takes place now. BTW, please come up with some goth bands and movies If u notice I used some of the gothic bands! PS: NO PREPS.

After dinner Eternity had to go back into a line with the first-years (she was part of them but much older) and Draco and another girl lead them upstairs into the Slytherin dorm. (a/n: in this story Draco and Pansy r cousins.) Eternity got to go to the front of the line to talk to Draco. She plunged her booted feet onto the stone floor and did so until she was at the front of the line

The other girl talking to Draco was had long ebony locks with blue streaks in them. She wore lots of white foundation and black eyeliner. She looked just like the girl in Linkin Park's video for Crawling.

(a/n: Eternity looks more like Amy Lee.) \enquote{What's your name?} Eternity asked. \enquote{I'm Pansy Parkinson. Well, that's what my motherfucking parents called me. Call me Sea.} she replied. \enquote{And I'm Eternity.} said Eternity. Draco just smiled shyly at Eternity through his silvery-blue eyes and black hair.

They walked upstairs to the dorms. Eternity couldn't help noticing that the castle looked a lot like the one in Dracula. As she, Draco, Sea and the first-years went up the stairs, a lot of preps from other houses stared at them looking scared.

A girl with brown hair and brown eyes kept staring at them. She was talking (probably about cheerleading or some shit like that) with a girl with long blonde hair. Eternity stuck her middle finger up at the girls. The girls gasped, their eyes got big, and they turned around. \enquote{Who the hell were they?} Eternity asked Draco. \enquote{Hermione Granger. The girl next to her was Luna Lovegood.} said Draco. \enquote{They're such goddamn bitches.} said Sea. \enquote{And the biggest fucking preps ever.} added Draco. Eternity couldn't help but agree.

They stopped at a portrait. It was of a girl with pale skin, long black hair, and black nails. She was the splitting image of the lead singer of Sisters of Mercy. \enquote{What the fuck? Why aren't we at the door?} asked Eternity. \enquote{Password?} asked the girl. \enquote{Bleeding kisses.} Draco said to the girl. \enquote{Correct.} said the girl and the portrait swung back to reveal a hole The first-years, Draco and Sea stepped inside. Eternity did too.

Suddenly, she was face-to-face with Gerard Way. \enquote{Oh my fucking god! I so fucking love your band!} she screamed. \enquote{Huh?} asked Gerard. \enquote{Hold on, hold on. That's not Gerard.} Elvira laughed. \enquote{That's Satan. Everybody says he looks like Gerard.} said Shadow. \enquote{Not that that's a bad thing!} said Darren. \enquote{Dude, I love MCR.} said Satan laughingly. Eternity smiled and shook their pallid hands.

Satan had long black hair up to his chin, just like Gerard.His eyes were pale blue and misty, like tears Eternity cried every night. He wore black eyeliner and black nail polish.

\begin{sloppypar}
    \enquote{Do you happen to like Slipknot or Sisters of Mercy?} asked Eternity in a flirty voice. \enquote{They kick ass!} agreed Satan. He and Eternity immediately began talking. The night went on really well. Eternity and her new friends talked about bands like Slipknot, MCR, Evanescence, GC, Marilyn Manson, Sisters of Mercy, Bauhaus, Dead Can Dance, Christian Death, Joy Division, the Cure, Siouxsie and the Banshees, Clan of Xymox, Fields of the Nephilim, Southern Death Cult, 45 Grave, X-mal Deutschland, Garden of Delight. They all agreed that they rocked and they all hated shitty pop bands like BSB and Play.
\end{sloppypar}

They used razors to slit their wrists when they felt depressed. The crimson regret flowed out on their pale white skin. They gave each other makeovers with black eyeliner, white foundation and lipstick and they read Dracula and Point Horror books out loud to each other with all the lights turned out and only flashlights.

Eternity felt overjoyed. Just a week ago she had been the only person in her school who had dyed black hair and black eyeliner instead of lip gloss and blonde hair, liked Slipknot or Linkin Park or MCR rather than Hilary Duff or Destiny's Child, slit her wrists, thought about suicide, shopped at Hot Topic instead of Limited Too, swore, or was depressed. Now there were so many wonderful people just like her. She was ecstatic.