\section{The Beautiful People}

\AN[a/n: ]{if ur a prep, DON'T READ THIS STORY. If you're not please help me out by suggesting some goth bands and movies for me to reference. Thanx.}

After the train ride Eternity and the other students got off the train. Eternity was shocked. In front of her was a beautiful castle. A very tall bearded man asked them to follow him into little boats.

Draco waved good-bye to Eternity and made death's touch sign (\AN[a/n: ]{if u don't know what that is I suggest u fuck off to a Britney Spears concert or something}).

Eternity and the others trooped inside the big castle. \enquote{Is this the school?} she asked a fourth-year next to her. \enquote{It's beautiful.} said Eternity. \enquote{You think that's beautiful?} a preppy first-year girl with blonde hair wearing a Hilary Duff t-shirt asked. \enquote{Why the fuck not?} Eternity asked defensively. \enquote{Yuck, it looks scary to me.} said the girl and Eternity rolled her eyes. \enquote{Ignore her. She's just another stuck-up prep.} said another girl next to Eternity.

Eternity looked at the girl. She was pretty and she looked about fifteen and had long black hair with purple streaks up to her waist with one forest-green eye and one blue one. She was wearing a long flowing black dress under her school uniform and fishnets and combat boots underneath that. \enquote{What's your name?} Eternity asked her. \enquote{Fillipa (\AN[a/n: ]{Filly there's a shout-out 2 u girlfriend!}) Clarke. Call me Filly if you want. But my middle name's Shadow. You could call me that too.} she said. They shook hands. Then they had to separate because Eternity had to follow Hagrid and the first-years into a magnificent hall. Banners were draped everywhere and there were four long tables in the room.

An old man with a long beard introduced himself \enquote{I am Professor Dumbledore. Welcome back.} he said. He made a long speech and then he brought out an old wrinkly hat to sort them into houses. \enquote{Let the sorting begin!} he announced. Eternity gasped then, because the hat burst into song. after he sang the song, everyone clapped. The sound of applause filled the large room. Some people went down to be sorted.

\begin{sloppypar}
    When it was Eternity's turn, she sat down nervously on the wooden chair and her heart beat like thunder. \enquote{Slytherin!} shouted the hat. Happiness filled Eternity. How could it be?
\end{sloppypar}

Draco looed at her his grey blue eyes filled with joy. Eternity shruged and sat down at the Slytherin table next to Shadow. The night went on and Hogwarts had a feast. Meanwhile Shadow introduced Eternity to her friends. (Draco was one of them.) She pointed to a girl with long purple hair with black tips wearing ripped jeans and an Atreyu t-shirt (a/n: that's u, Tara!). \enquote{That's Elvira.} she said. Then she introduced Eternity to another boy with black hair and green eyes. \enquote{Hey, bitch.} grinned Elvira. \enquote{And that's Darren. He's a half-vampire.} she said, pointing to the boy. \enquote{Hi.} said Darren.

The four of them talked about Marilyn Manson and the Underworld movies for a while and made fun of Christina Aguilera and Hilary Duff. Then, it was time to go to the dormitories.