\section{Bring me to Life}

\begin{sloppypar}
    Eternity woke up the next morning. She brushed her teeth, combed her hair, and then went to her closet. She put on a long black dress that was all ripped and torn, with pink stuff underneath (kind of like the one Amy Lee wore to the Grammies) and then put on big black combat boots. Shadow, Elvira and Sea all got up and
\end{sloppypar}

\enquote{You are so lucky, bitch.} moaned Shadow while she put on her own clothes (a long black dress with a corset at the top, pointy high-heeled boots, and fishnets). \enquote{You have such a great body.} added Sea, putting on a ripped black dress with no sleeves that looked exactly like the one the lead singer of her favorite goth band had worn to the MTV awards that year. (Elvira put on a long black velvet dress with crimson lace.)

Eternity laughed but secretly she knew what her friends meant. They were all skinny, but not as much as her, and they all had size-B bras.

She sadly put her hair up in a messy half-bun (kind of like Amy Lee has in the video for 'Going Under.') put on tons of eyeliner and black lipstick, and went downstairs with her friends.

\begin{sloppypar}
    At the breakfast table, she ate Count Chocula cereal and drank red wine even though it was only breakfast. Darren had made a request for human blood, so he drank that and let his friends try some.
\end{sloppypar}

They all clinked their glasses. \enquote{To depression.} said Eternity.

\enquote{To darkness.} said Satan.

\enquote{To vampires.} said Sea.

\enquote{To heavy metal music.} said Shadow.

\enquote{To Eternity.} said Draco.

Everyone started giggling, except for Draco. Eternity's pale complexion turned red. Everyone went off to their classes. Eternity hated all of the classes, even though she was good at them.

In Transfiguration class, Eternity had to sit next to a bunch of giggling blonde girls. Their teacher, Professor McGonagall made a speech, and then made them practice transfiguration on a bunch of ants they would try to turn into pencils.

Everyone was trying, but it didn't work for them. Suddenly, Eternity found herself pointing to the ant and saying a spell… Suddenly, the ant turned into a gigantic black unicorn with huge black wings and flew out the window. Everyone in the room gasped. Later, Professor McGonagall had a talk with Eternity. \enquote{Eternity, you are being moved up to your fifth year.} she said.