\chapter{Ghost of You}
\chapterauthor{bloodytearz666}

\section{Helena}

\AN[Disclaimer: ]{Um okay I don't own this lolz. Coauthored with xxxbloodyrists666xxx.}

\AN[a/n: ]{the other story got a bit boring so here goes and if you're one of the fuckers who flamed Tara's story u can go 2 hell, cause she helped with this. I don't give a fuck when HP takes place. This takes place NOW, and it's MY story, so they can have iPods and NORMAL clothes and shit if I want them 2. So if you're against goths or a prep or something then do everyone a favor and fuck off.}

Hermoine Granger checked her black lipstick in her black makeup mirror as she trudged her way to the Hogwarts Express. Last year, she probably would have seen a freak with a bushy mass of hair and brown eyes.

\begin{sloppypar}
    But after the events of this summer, she certainly didn't. Hermione had changed over the summer. Her parents had revealed to her during their summer vacation in America that they were not in fact her parents at all, rather, both her parents were wizards- and she had been adopted by the Grangers- the Grangers, who had spat on her, abused her, neglected her for so long (Note: And yes, this is possible because it is never implied that it's NOT true.) The nights Hermoine had spent suffering in her room, whishing it would all stop…They refused to reveal to her who her parents were and why she had been abandoned. In her rage, Hermione- or Maya, as she was now called- had murdered them, using magic. This was unknown to the Ministry. Hermione spent the rest of the summer in Tokyo at Cho's apartment with her and Ginny. She had grown very close to both of them.
\end{sloppypar}

Now as she embarked the train to her sixth year, Maya swished her nearly waist-length, newly dyed raven locks and blinked her emerald- with the use of magic- eyes as she stepped into a seat on the Hogwarts Express. She wore a black leather bustier, a blue plaid mini trimmed with black lace, ripped black fishnets and black lace-up platform boots. On her face was lots and lots of black eyeliner, blood-red lipstick, and matching eyeshadow. Her skin was pale white from the lack of sunlight, and she was slender, but with curves in all the right places. She took out her iPod and put on an Evanescence song at full volume. Some preps stared at her.

\enquote{Oh my like god, what are you, like, listening to?} gasped Luna, who was sitting on another seat with a bunch of giggly blonde preps wearing a pink mini, a slutty pink halter top and Gucci shoes. She looked exactly like Hilary Duff. Some preps next to her giggled. Maya stuck up her white-skinned middle finger at them. Hermoine went back to listening to her iPod. She changed the song to an My Chemical Romance one and tried to drown out the prep's voices by listening to Gerard's incredible, sexy voice and thinking about him. Suddenly, someone tapped her on the shoulder. \enquote{Fuck!} she screamed.

She looked behind her. Virginia (there's u Tara luvya gurl lolz!) and Cho, whose nickname is Dementia after her middle name, (Filly u rock bitch, MCR rock 666!1) were standing next to her, looking excited. Ginny was wearing a sexy black corset dress with red lacing, pink fishnets and black high heeled boots. She was wearing black lipstick and eyeliner and her hair was dyed blood-red, with black tips.

Dementia had new purple streaks in long, silky ebony hair and was wearing a torn black MCR t-shirt, a ripped black and red plaid mini, safety pin earrings and black combat boots with heels. \enquote{Well, that's nice.} said Dementia. \enquote{Oh, sorry. Sit down, my bitches.} Maya said jokingly. Her friends trooped in and sat next to her. Maya noticed now who she was sitting behind- Draco Malfoy. As he heard her voice, he looked around coyly for a split-second and then looked back. His hair was dyed black and slicked back (a/n: kinda like Tom Felton in the first movie). His eyes were icy blue and suggested inner depths of darkness.

Maya and the girls high-fived and chatted for a while. After some time, Ginny asked, \enquote{So have you seen the guys?} \enquote{You mean Harry and Ron? No.} said Maya.\enquote{Well, you better find them soon because they're gonna be lovin' your new look.} said Dementia.

Just then, the train stopped. The girls got out, grinning, freaking out preps. Maya didn't see Harry or Ron, but she just might have seen a boy in leather pants, a leather jacket, black hair and blue eyes smile at her. 
