\section{}

\AN{stop f,aing ok hargrid is a pedo 2 a lot of ppl in amerikan skoolz r lik dat I wunted 2 adres da ishu! how du u no snap iant kristian plus hargrid isn't really in luv wif ebony dat was sedric ok!}

\XXX{XXXXXXXXXXXXX666\Xfill}

I was about to slit my wrists again with the silver knife that Drago had given me in case anything happened to him. He had told me to use it valiantly against an enemy but I knew that we must both go together.

\enquote{NO\@!} I THOUGHT IT WAS HAIRgrid but it was Vampire. He started to scream. \enquote{OMFG\@! NOOOOO\@! MY SCAR HURTS\@!} and then….. his eyes rolled up! You could only see his red whites.

I stopped. \enquote{How did u know?}

\enquote{I saw it! And my scar turned back into the lightning bolt!}

\enquote{NO\@!} I ran up closer. \enquote{I thought you didn't have a scar anymore!} I shouted.

\enquote{I do but Diabolo changed it into a pentagram for me and I always cover it up with foundation.} he said back. \enquote{Anyway my scar hurt and it turned back into the lightning bolt! Save me! then I had a vision of what was happening to Draco\dotfill Volfemort has him bondage!}

Anyway I was in the school nurse's office now recovering from my slit wrists. Snap and Loopin and HAHRID were there too. They were going to St.~Mango's after they recovered cause they were pedofiles and you can't have those fucking pervs teaching in a school with lots of hot gurlz. Dumbledore had constipated the cideo camera they took of me naked. I put up my middle finger at them.

Anyway Hargrid came into my hospital bed holding a bouquet of pink roses.

\enquote{Enoby I need to tell u somethnig.} he said in a v.\ serious voice, giving me the roses.

\enquote{Fuck off.} I told him. \enquote{You know I fucking hate the color pink anyway, and I don't like fucked up preps like you.} I snapped. Hargrid had been mean to me before for being gottik.

\enquote{No Enoby.} Hargrid says. \enquote{Those are not roses.}

\enquote{What, are they goffs too you poser prep?} I asked cause I was angry that he had brought me pink roses.

\enquote{I saved your life!} He yelled angrily. \enquote{No you didn't I replied.} \enquote{You saved me from getting a Paris Hilton p- video made from your shower scene and being vued by Snap and Loopin.} Who MASTABATED (c is dat speld rong) to it he added silently.

\enquote{Whatever!} I yelled angirly.

He pointed his wand at the pink roses. \enquote{These aren't roses.} He suddenly looked at them with an evil look in his eye and muttered Well If you wanted Honesty that's all you haD TO SAY! .

\enquote{That's not a spell that's an MCR song.} I corrected him wisely.

\enquote{I know, I was just warming up my vocal cordes.} Then he screamed. \enquote{Petulus merengo mi kremicli romacio(4 all u cool gof\-fic mcr fans out, there, that is a tribute! specially for raven I love you girl!)imo noto okayo!}

And then the roses turned into a huge black flame floating in the middle of the air. And it was black. Now I knew he wasn't a prep.

\enquote{OK I believe you now wtf is Drako?}

Hairgrid rolled his eyes. I looked into the balls of flame but I could c nothing.

\enquote{U c, Enobby,} Dumblydore said, watching the two of us watching the flame. \enquote{2 c wht iz n da flmes(\AN[]{HAHA U REVIEWRS FLAMES GEDDIT}) u mst find urslf 1st, k?}

\enquote{I HAVE FOUND MYSELF OK YOU MEAN OLD MAN\@!} Hargrid yelled. dUMBLydore lookd shockd. I guess he didn't have a headache or else he would have said something back.

Hairgrid stormed off back into his bed. \enquote{U r a liar, prof dumbledoree!}

Anyway when I got better I went upstairs and put on a black leather minidress that was all ripped on the ends with lace on it. There was some corset stuff on the front. Then I put on black fishnets and black high-heeled boots with pictures of Billie Joe Armstrong on them. I put my hair all out around me so I looked like Samara from the Ring (if u don't know who she iz ur a prep so fuk off!) and I put on blood-red lipstick, black eyeliner and black lip gloss.

\enquote{You look kawai, girl.} B'loody Mary said sadly. \enquote{Fangs (geddit) you do too.} I said sadly too, but I was still upset. I slit both of my wrists feeling totally depressed and I sucked all the blood. I cried again in my bathroom and put the shades on so Snap and Loopin couldn't spy on me this time. I went to some classes. Vampire was in the Hair of Magical Magic Creatures. He looked all depressed because Draco had disappeared and he had used to be in love with Draco. He was sucking some blood from a Hufflepuff.

\enquote{Hi.} he said in a depressed way. \enquote{Hi back.} I said in an wqually said way.

We both looked at each other for some time. Harry had beautiful red gothic eyes so much like Dracos. Then\dotfill we jumped on each other and started screwing each other.

\enquote{STOP IT NOW YOU HORNY SIM\-PLE\-TONS\@!} shout\-ed Professor McGoggle who was watching us and so was everyone else.

\enquote{Vampire you fucker!} I said slapping him. \enquote{Stop trying to screw me. You know I loved Draco!} I shouted and then I ran away angrily.

Just then he started to scream. \enquote{OMFG\@! NOOOOO\@! MY SCAR HURTS\@!} and then\dotfill his eyes rolled up! You could only see his red whites.

\enquote{NO!} I ran up closer.

\enquote{I thought you didn't have a scar anymore!} I shouted.

\enquote{I do but Diabolo changed it into a pentagram for me and I always cover it up with foundation.} he said back. \enquote{Anyway my scar hurt and then I had a vision of what was happening to Draco\dotfill\\.\dotfill Volfemort has him bondage!}

\XXX{\Xfill 666XXXXXXXXXXX}

\AN[]{SPECIAL FANGZ 2 RAVEN MY GOFFIX BLOOD SISTA WTF UR SUPPOZD 2 RIT DIS!11111111

HEY RAVEN DO U KNOW WHERE MY SWEATER I}
