% !TeX root = ../my_immortal.tex
\section{}

\AN{I sed shut da fok up u quiephs!111 stop kalin ebony a mary su ok u dnot even no wutz gong 2 happen ok so fuk u!1111 fangz 2 muh bff raven 4 di help!1111}

\XXX{\Xfill 666XXXX\Xfill}

\enquote{I always knew u were on Voldemort's side, you sun of a bitca (\AN[]{\makeEndnote{bufy}{buffy}{Likely a reference to Buffy, the titular character of the \citetitle{buffy} film and television series.} rox!111}).} Serious said 2 Snape.

\enquote{No I'm not I was teaching them somefing!1} Snap clamed.

\enquote{Oh fucking yeah?} I took some blak Volremortserum out of my poket and gave it to Serverus. He made Snap dirnk it. He did arngrily. Then Luscious took out a tape recorder and started playing it while he did curses on Snap. Then Proffesor Sinister and Lucian made us get out wif them while Snape told his secretes. Lucian took Vampure and Draco to the nurse after thanking me a millon times. Profesor Trevolry took me to a dark room. Now I wuz going to go back in time to sedouce Volxemort. Moving posters of MCR and Nrivana were all over. Hermoine, Darkness and Willow came too. B'loody Mary gave me a blak bag from Tom Rid's store.

\enquote{Whatz in da bag?} I asked Profesor Trevolry.

\enquote{U will c.} she said. I opened thee bag. In it was a sexy tite low-smut black leather gothic dress. It had red korset stuff and there was a silt up da leg. I put it on. My frendz helped me put on blak fishnetz and blak pointy boots Willow had chosen. Willow and Darkness helped me put on black eyeliner and blod-red lipshtick.

\enquote{You look fucking kawaii, bitch.} B'loody Mary said.

\enquote{Fangs.} I said.

\enquote{Ok now you're going to go back in tim.} said Proffesor Sinister. \enquote{U will have to do it in a few sessionz.} She gave me a blak gun. I put it in a strap on my fishnetz like in \makeEndnote[Redisnet Evill]{Redisnet Evill.}{resident_evil}{Video game and film franchise \citetitle{resident_evil} follows characters fighting hordes of zombies.} Then she gave me a black time-tuner. \enquote{After an hour use da time torner to go back here.} Proffesor Trevolry said. Then she and B'loody Mary put a Pensive in front of me. Every1 went in front of it.

\enquote{Good luk!1} Everryone shooted. Darkess and Willow gave me deth's touch sin. Then\dotfill I jumped sexily in2 da Pensive.

Suddenly I was in fornt of teh School. In front of me wuz one of da sexiest goth guyz I had ever seen. He was wering long blak hair, kinda like Mikey Way only black. He had gren eyes like Billie Joe Amstrung and pale whit skin. He wuz wearing a blak ripped up suit wif Vans. It was\dotfill \makeEndnote[Tom Bombodil]{Tom Bombodil!1111}{bombodil}{Tom Bombadil is an engimatic character in \citefirstlastauthor{lotr}'s mythology, best known for an appearance in \citetitle{lotr-fellowship}. The immediately following author's note claims this is a \enquote{mistak} and the name is never used again, complicating interpretation of why it appears in \citetitle{my_immortal}.}
