\section{}

\AN{I sed stup fflaming I no his nam iznt tom bodil dat wuz a mistak!1111 if u dnot lik de story den u kan go skrew urself!11111 U SUK!111111}

\XXX{\Xfill XXXXXX666\Xfill}

\enquote{Hi.} I said flirtily. \enquote{Im Enoby Way da new student.} I shok my pale handz wif their blak noil polish wif him.

\enquote{Da name's Tom.} he said. \enquote{But u kan call me Satan. Datz ma middle nam}

We shok hands. \enquote{Well come on we have 2 go upstairs.} Satan said. I followed him. \enquote{Hey Satan\dotfill\newline
do u happen to be a fan of Gren Day?} (sinz mcr and evinezenz dont exist yet den) I asked.

\enquote{Oh my fuking god, how did u know?} Satan gasped. \enquote{actually I like gc a lot too.}(geddit coz gc did that song I just wanna live that's ounded really 80s)

\enquote{omg me too!} I replied happily.

\enquote{guess what they have a concert in hogsment.} satan whispered.

\enquote{hogsment?} I asked.

\enquote{yeah that's what they used to call it in these time before it became Hogsmeade in 2000.} he told me all sekrtivly. \enquote{and theres a really cool shop called Hot-\enquote{

`topic!}} I finshed, happy again.

\begin{sloppypar}
    He froned confusedly. \enquote{noo its called Hot Ishoo.} He smiled skrt\-vli again. \enquote{then in 1998 dey changd it to hot topic.} he moaned.
\end{sloppypar}

\enquote{ohh.} now everything was making sense for me. \enquote{so is dumblydor your princepill?} I shouted.

\enquote{uh-huh.} he looked at his black nails. \enquote{im in slitherin'}

\enquote{OMfG SHME TOO\@!} I SHRIEDKED.

\enquote{u go to this skull?}(geddit cos im goffik) he asked.

\enquote{yah that's why im here im NEW.} I SMELLED HAPPili.

Suddenly dumblydore flew in on his broomstuck and started shredding at us angrily. \enquote{NO TALKING IN THE HALLS\@!} he had short blonde hair and was wearing a polo shirt from Amrikan ogle outfters. \enquote{STUPID GOFFS\@!}

satan rolled his eyes. \enquote{his so mean to us goffs and punks just becose we're in slytherine and we're not preps.}

I turned around angrily. \enquote{actually I fink mebe its becos ur da barke lord.}

\enquote{wtf?} he asked angrily.

\enquote{oh nuffin.} I said sweetly.

then suddenlyn\dotfill the floor opened.\newline
\enquote{OMFG NO I SCEAMED AS I FEEL DOWN\@. everyone looked At ME weirdly.}

\enquote{hey where r u goin?} satan asked as I fell.

I got out of the hole n it was bak in the pensive in professor trevolry's classroom. dumblydum wuz dere. \enquote{dumblydore I think I just met u.} I said.

\enquote{oh yeah I rememba that.} dumblydor said, trying to be all goffik.

sinister came in. \enquote{hey dis is my classroom wait wtf enoby what da hell r u doing?}

:\enquote{um.} I looked at her.

\enquote{oh yeaH I forgot bout that.}

\enquote{wth how?} I screamed forgetting she was a teacher for a second. but shes a goff so its ok.

professor sinster looked sad. \enquote{um I was drinking voldemortserum.} she started to cry black tears of depression. dumblydum didn't know about them.

\enquote{hey r u crying tears of blood?} he asked curiously, tuching a tear.

\enquote{fuck off!} we both said and dumblydum took his hand away.

professor sinster started crying again in her chair, sobbing limp\-id tears. \enquote{omfg enoby\ldots{} I think im addicted to Voldemortserum.}

\AN{SEE U FOKKING PREPZ GO FOK URSELXXZ DATZ SERUS ISSUZ 2O GO 2 HELL!1111112}
