% !TeX root = ../my_immortal.tex
\section{}

\AN{I sed stop flaming ok!111111111 I bet u r al proly old srevinty yr oldz!111 ps PORTERSUZ UR A PREP!1 o ya nd fangz 2 raven 4 di help!111 hav fun in englond gurl!11111}

\XXX{\Xfill 666\Xfill}

I loked around in a depresed way. Suddenly I saw Profesor Sinister. B'lody Mary, Socrates and Draco, Vampire and Willow were their to.

\enquote{OMFG Sorius I saw u nd Samaro and Snip nd everyone!11111 I kant beleev Snap uzd 2 b goffik!111111}

\enquote{Yah I no.} Serious said sadly.

\enquote{Oh hey there bitch.} Profesor Trevolry said in an emo voice dirnking some Volxemortserom.

Hi fuker.'' I said. \enquote{Lizzen, Satan asked me out to a gottik cornet and a movie so I need a sexah new outfit for da date. Also I'm playng in a gothic band so I need an ootfit for that too.}

\enquote{Oh my satan!1} (geddit lolz koz shes gofik) gasped B'lody Mary. \enquote{Want 2 go to Hot Topik to shop 4 ur outfit?}

\begin{sloppypar}
    \enquote{OMFS, letz have a groop kutting session!11} said Profesor Trevolry.    
\end{sloppypar}

\enquote{I can't fucking wait 4 dat but we need 2 get sum stuff first.} said Willow.

\enquote{Yah we need sum portions for Profesor Trevolry so she wont be adikted 2 Volxemortserum anymore nd also………….sum luv potion 4 Enoby.} Darko said resultantly.

\enquote{Well we have potions klass now.} Willow said so let's go.

We went sexily to Potionz class. But Snap wasn't there. Instead there was\dotfill Cornelio Fuck!11111

\enquote{Hey where the fuck is Dumblydore!111} Draco shouted angrily.

\enquote{STFU\@!\@1\@}\@ shooted Cornelia Fuck. ``He is in Azkhabian now wif Snip and Loopin he is old and week he has kancer. \enquote{Now do ur work!111}

My friendz and I talked arngrily.

\enquote{Can you BELEVE Snap used to be gottik!1} Vampire asked surprisedly.

\enquote{DATZ IT!11} CORNELIO FUK SHOOTED ARNGRILY\@. \enquote{IM GETTING PROFESOR BRIDGE!111}

He stomped out angrily.

Mi frendz and I began talking again. I began to drink some blod mixed wif beer. Suddenly I saw Hargrid in da cupboard.

\begin{sloppypar}
    \enquote{WTF is he doing?} I asked. Then I looked at Draco. He wuz wearing tonz of eyeliner nd he locked shexier den eva. Suddenly\ldots\newline\dotfill\enquote{HARGRIF WUT DA FOK R U DOING!11} he shooted.
\end{sloppypar}

I looked around\dotfill Hairgrid wuz putting sumfing in my\newline glass of blod!11 Darko and Vampire started 2 beat him up sexily.

\enquote{God u r such a posr!1} I shooted at Hairgrid. Suddenly I looked ar what he was putting in da blood. It was\dotfill\newline Amnesia Portion!111
