% !TeX root = ../my_immortal.tex
\section{}

\AN{i sed stup flaming up prepz! c if dis chaptr is srupid!1111 it delz wit rly sris issus! sp c 4 urself if itz ztupid brw fangz 2 ma frend raven 4 hleping me!}

\XXX{XXXXXXXXXXXXXXXX666\Xfill}

\enquote{NO\@!} I screamed. I was horrorfied! B'loody Mary tried to comfort me but I told her fuck off and I ran to my room crying myself. Dumbledore chased after me shouting but he had to stop when I went into my room cause he would look like a perv that way.

Anyway, I started crying tears of blood and then I slit both of my wrists. They got all over my clothes so I took them off and jumped into the bath angrily while I put on a Linkin Park song at full volume. I grabbed a steak and almost stuck it into my heart to commit suicide. I was so fucking depressed! I got out of the bathtub and put on a black low-cut dress with lace all over it sandly. I put on black high heels with pink metal stuff on the ends and six pairs of skull earrings. I couldn't fucking believe it. Then I looked out the window and screamed\ldots{} Snap was spying on me and he was taking a video tape of me! And Loopin was masticating to it! They were sitting on their broomsticks.

\begin{sloppypar}
    \enquote{EW, YOU FUCKING PERVS, STOP LOOKING AT ME NAKED! ARE YOU PEDOS OR WHAT\@!} I screamed putting on a black towel with a picture of Marilyn Mason on it. Suddenly Vampire ran in.
\end{sloppypar}

\begin{sloppypar}
    \enquote{Abra Kedavra!} he yelled at Snape and Loopin pointing his womb. I took my gun and shot Snape and Loopin a gazillion times and they both started screaming and the camera broke. Suddenly, Dumblydore ran in. \enquote{Ebony, it has been revealed that someone has -- NOOOOOOOOOOOOO\@!} he shouted looking at Snape and Loopin and then he waved his wand and suddenly\ldots{}
\end{sloppypar}

Hargrid ran outside on his broom and said everyone we need to talk.

\enquote{What do you know, Hargrid? You're just a little Hogwarts student!}

\enquote{I MAY BE A HOGWARTS STUDENT\ldots{}} Hargirid paused angrily. \enquote{BUT I AM ALSO A SATANIST\@!}

\enquote{This cannot be.} Snap said in a crisp voice as blood dripped from his hand where Dumblydore's wand had shot him. \enquote{There must be other factors.}

\enquote{YOU DON'T HAVE ANY\@!} I yelled in madly.

Loopin held up the camera triumelephantly. \enquote{The lens may be ruined but the tape is still there!}

I felt faint, more than I normally do like how it feels when you do not drink enough blood.

\begin{sloppypar}
    \enquote{Why are you doing this?} Loopin said angrily while he rubbed his dirty hands on his clook.
\end{sloppypar}

And then I heard the words that I had heard before but not from him. I did not know whether to feel shocked and happy or to bite him and drink his blood because I felt faint.

\enquote{BECAUSE\ldots{} BECAUSE\ldots{}} Hargid said and he paused in the air dramitaclly, waving his wand in the air. Then swooped he in singing to the tune of a gothic version of a song by 50 Cent.

\enquote{Because you're goffic?} Snap asked in a little afraid voice cause he was afraind it meant he was connected with Satan.

\enquote{Because I LOVE HER\@!}
