\section{gost of u}

\AN{fangz 2 suzi 4 da idea!1 u rok! fuk of prepz!11111111 fangz 2 raven 4 di help u rok gurl!1 ps im gong 2 end da stroy rlly sun so FUK U!111 oh yah nd if u no eny gofik namz plz tel me koz I ned 1 4 serius!1 fangz.}

\XXX{\Xfill 666\Xfill}

I went in2 da Conmen Room finking of Satan. Suddenly I gasped\dotfill Draco wuz there!111

I grasped. He locked as hut as eva werring blak ledder pants, a blak Lonken Prak t-shrit and blak eyeliner.

\enquote{Draco what da fuk r u dong!111111} I gosped.

\enquote{Huh?} he asked. Then I remembred. It wuzn't Draco. It was Lucan!1 He stil had two arms.

\enquote{Oh hi Lucian!1} I sed. \enquote{Im Ebony the new student lol we shook handz.}

\enquote{Yah Satan told me abot you.} Lusian said. He pinted to a groop of sexxxy gottik guyz. They where siting in a corner kutting. It wuz Serious, Vampire's dad and\dotfill Snap! All of them\newline were wearing blak eyeliner and blak Good Chralootte band shirts. \enquote{Lizzen I'm in a goth band wif those guys.} he said. \enquote{Were playing 2nite at da Marylin Mason show as back-up.}

\enquote{ORLY.} I ESKED\@.

\enquote{Yeah.} he said. \enquote{Were calld XBlakXTearX. I play teh gutter. Spartacus plays da drums} he said ponting to him. \enquote{Snap plays the boss. And Jamez plays the guitar to even fo we call him Samaro, after Samara in da ring.}

\enquote{Hey bastards.} I told them they gave me Dethz tuch sin. Suddenly I gasped again. \enquote{But don't u have a lead singer!} I asked. Lucian looked dawn sadly.

\enquote{We uzd to but she did. She contempted suicide by silting her rists.}

\enquote{Oh my fuking god!11 Datz so fuking sad!1} I gasped.

\enquote{Its okay but we need a new led snigger.} Samaro said.

\enquote{Wel\dotfill I said Im in a bnad myself.}

\enquote{Rilly?} asked Snap. I cudnt belive it. He used 2 b goffik!111

\enquote{Yeah were called Blody Gothik Rose 666. Do u wanna hr me sing?}

Yeah said everyone. So the guys tok out der guitarz. They began to pay a song bi (geddit koz bi guyz r sooo sexah!11) Gurn Day.

\enquote{I wok dis empt stret on da bolevrad of broken dremz.} I sang sexily (I dnot own da lyrikz 2 dat song).. Every1 gasped.

\enquote{Enopby? Will u join da band? Plz!1} begged Lucian, Samoro, Serious and Snap.

\enquote{Um\ldots{}\ldots{} ok.} I shrugged. \enquote{Are we gong to play tonight?}

\enquote{Yah.} they said.

\enquote{Ok.} I said but I new dat I had 2 get a new outfit. I walked outside wondering how I kud go forward in time. Suddenly someone jumped in fornt of me. It wuz\ldots{}\ldots{} Morty Mcfli!1 He was wering a blak bnad tshrit and blak bagy jeans.

\enquote{What da hell r u dong here!11} I asked.

\enquote{I wil help u go frowad in tim Enoby.} he said siriusly Den\dotfill\newline he took out a blak tim machine. I went in2 it and\dotfill\newline sudenly I wuz forward in tim!111

