\section[im nut ok i promise]{\protect\makeEndnote{im nut ok i promise}{mcr-not_okay-2}{See note to page~\pageref{enl:mcr-not_okay}.}}

\AN{plz stup flaming da story if u do ur a foken prep n ur jelous ok!11 frum noq un im gong 2 delt ur men reviowz!111 BTW evonyd a poorblod so der!1 fangz 2 raven 4m da help!11}

\XXX{\Xfill 666\Xfill}

All day we sat angerly finking about Dumbelldore. We were so fucking pissed off. Well, I had one thing to look forward too- da MCR concert. It had been postphoned, so we could all go.

\begin{sloppypar}
    Anyway, I went to the common room sadly to cut classes. Draco was being all secretive.
\end{sloppypar}

I asked what it was and he got all mad me and started crying all hot and angsty (rnt sensitve bi guyz so hot).

\enquote{No one fucking understands me!1} he shouted angrily as his black hare went in his big blue eyes like Billie Joe in Boulevard of Borken Dreamz. He was wearing black baggy paints, a black MCR t-shirt and a black die. (geddit insted of tie koz im goffik) I was wearing a blak leather low cut top with chains all over it all over it a blak leather mini, black high held boots and a cross belly fing. My hair was al up in a messy relly high bun like Amy Lee in Gong Under. (email me if u wana see da pik)

\enquote{Accuse me? What about me!} I growled.

\enquote{Buy-but-but-} he grunted.

\enquote{You fucking bastard!} I moaned.

\enquote{No! Wait! It's not what it fucking looks like!} he shouted.

But it was to late. I knew what I herd. I ran to the bathroom angrily, cring. Draco banged on the door. I whipped and whepped as my blody eyeliner streammed down my cheeks and made cool tears down my feces like Benji in the video for Girls and Bois (raven that is soo our video!). I TOOOK OUT A CIGARETE END STARTED TO smoke pot.

Suddenly Hargrid came. He had appearated.

\enquote{You gave me a fucking shock!} I shouted angrily dropping my pot. \enquote{Wtf do you fink you're doing in da gurl's room?}

Only it wasn't just Hargrid. Someone else was with him too! For a second I wanted it 2 b Tom Rid or maybe Draco but it was Dumblydore.

\enquote{Hey I need to ask you a question.} he said, pulling out his black wanabe-goffik purse. \enquote{What are u wearing to the concert?}

\enquote{U no who MCR r!} I gasped.

\enquote{No I just saw there was a concert dat a lot of gothz and punx were going 2.} He said. \enquote{Anyway Draco has a surprise for u.}

