\section{}

\AN{SHOT DA FOK UP PREPZ!1111 hav u even red de story!11 u r proly al just prepz nd posrs so FUK U!111 fangz 2 raven 4 da help!1}

\XXX{\Xfill 666XXXXXXXXXXX}

I wook up in da coffin de next day. Draco waz gone. I got up and put on a blak tight sexah drsss that was all ripped at da end. There wuz red korset stuff going up da fornt and da bak and it came up 2 my knees. There wuz a slit in da dress lik in mr \& mr~simth. I pot on ripped blak fishnets and blak stilton bo-ots. Suddenly\dotfill Sorious cocked on da door.\newline I hopened it.

\enquote{Hi Ibony.} he said. \enquote{Gezz wut u have 2 cum 2 Profesor Sinistor's office.}

\enquote{Ok.} I said in a deprezzd voice. I had wanted to fuk Draco or maybe lessen to MCR or Evonezcence. I came anyway.

\enquote{So what the fuck happened 2 Snipe and Loopin?} I asked Sorious flirtily.

\enquote{I fucking tortured them.} he answered in a statistic way. \enquote{They r in Abkhazian now, lol.}

I laughed evilly.

\enquote{Where r Draco and Vampira?} I muttered.

\enquote{Dey are xcused form skool 2day.} Sodomize moaned sexily. \enquote{Rite now they are watching Da Nigtmare b4 Xmas.}

We went into da office. Proffesor Sinister was there. She was wearing a goffik blak dress that was all ripped all over it kinda lik da one Amy Lee wears in this pic

( http/ She wuz drinking some Volximortserum.

She took out da Pensiv and the time-torner.

\enquote{Enoby, you will have to do anozzer session now. Also I need u to get me da cure 4 being adikited.} she said sadly. \enquote{Good luck. Fangz!}

And then\dotfill I jumped into the Prinsive again.\newline
Suddenly I looked around\dotfill I was in da Grate Hall\newline
eating Count Chorcula. It was mourning. I was sitting next to Satan. On a table was a tall gottik man wif long blak hair, pail skin and blue eyes wering a suit and blak Cronvrese shoes. He looked just like Charlyn Manson. I noticed\ldots{}\ldots{} he was drinking a portent.

\enquote{Whose he!11} I asked.

\enquote{Oh, datz Profesor Slutborn.} Satan said. \enquote{He's da Portents teacher\dotfill Ebony?}

\enquote{Yah?} I asked.

\enquote{Did u know dat Marylin Mason is playing in Hogsemade to\-night? And they r showing The Exercise at da movies b4 dat.}

\enquote{Yah?}

\enquote{Wel\dotfill want 2 go 2 da contort and da movie wif me?}
