% !TeX root = ../my_immortal.tex
\chapter{My Immortal}
\chapterauthor{XXXbloodyrists666XXX}

\section{}

\AN{Special fangz (get it, coz Im goffik) 2 my gf
(ew not in that way) raven, bloodytearz666
4 helpin me wif da story and spelling. U rok!
Justin ur da luv of my deprzzing life u rok 2!
\makeEndnote{MCR}{mcr}{My Chemical Romance, an
American emo band formed in 2001, popular in 2000s
alternative subcultures. They are mentioned
frequently in \citetitle{my_immortal}, as well as
are their individual members vocalist Gerard Way
and bassist Mikey Way. Their acclaimed
album \citetitle{MCR-black_parade} was commercially
successful in 2006--7 and lends its name to \chaptername~42.} ROX!}

\XXX{\Xfill}

Hi my name is Ebony Dark'ness Dementia Raven Way and I have long ebony black hair (that's how I got my name) with purple streaks and red tips that reaches my mid-back and icy blue eyes like limpid tears and a lot of people tell me I look like \makeEndnote{Amy~Lee}{amylee}{Lead vocalist of American rock band Evanescence.} (\AN{if u don't know who she is get da hell out of here!}). I'm not related to Gerard Way but I wish I was because he's a major fucking hottie. I'm a vampire but my teeth are straight and white. I have pale white skin. I'm also a witch, and I go to a magic school called Hogwarts in England where I'm in the seventh year (I'm seventeen). I'm a goth (in case you couldn't tell) and I wear mostly black. I love \makeEndnote{Hot~Topic}{hottopic}{American retail chain specializing in counterculture apparel.} and I buy all my clothes from there. For example today I was wearing a black corset with matching lace around it and a black leather miniskirt, pink fishnets and black combat boots. I was wearing black lipstick, white foundation, black eyeliner and red eye shadow. I was walking outside Hogwarts. It was snowing and raining so there was no sun, which I was very happy about. A lot of preps stared at me. I put up my middle finger at them.

\enquote{Hey Ebony!} shouted a voice. I looked up. It was\ldots{}\ Draco Malfoy!

\enquote{What's up Draco?} I asked.

\enquote{Nothing.} he said shyly.

But then, I heard my friends call me and I had to go away.

\XXX{\Xfill}

\AN{IS it good? PLZ tell me fangz!}
