\stepcounter{section}
\section{\chaptername~\thesection}

\AN{dhut da fok up biches!1 ur jus jelos koz I gut 10000 reviowz!1 fangz 2 raven 4 da help n telin me bout da boox gurlu rok letz go shopin 2getha!}

\XXX{\Xfill 666XXXXX\Xfill}

The door opened and Proffesor Rumbridge and Cornelia Fudge stomped out angrily. Then Dumbledum and Rumbridge sawed us.

\enquote{MR.~WAY WHAT THE BEEP ARE YOU DOING\@!} Rumbridge shouted angrily. Dumbledore blared at her.

\enquote{Oops she made a mistake!} he corrupted her. \enquote{She means hi everybody cum in!}

Well we all came in angrily. So did all the other students. I sat between Darkness and Draco and opposite B'loody Mary. Crab and Goyle started 2 make some morbid jokes. They both looked exactly like Ville Vollo. I eight some Count Chocula and drank som blood from a cup. Then I herd someone shooting angrily. I looked behind me it was\dotfill Vampire!\newline He and Draco were shooting at eachother.

\enquote{Vampire, Draco WTF?} I asked.

\enquote{You fucking bustard!} yelled Draco at Vampire. \enquote{I want to shit next to her!1}

\enquote{No I do!} shouted.

\enquote{No she doesn't fucking like u, you son of a bitch!} yelled Draco.

\enquote{No fuck you motherfucker she laves me not you!} shouted Vampire. And then\dotfill he jumped on Draco!\newline (no not in dat way u perv) They started to fight and beat up each other.

Dumbldore yelled at them but they didn't stop. All of a sudden\ldots\ldots a terrible man with red eyes and no nose flew in on his broomstick. He had no nose and was wearing a gray robe. All the glass in the window he flew thru fell apart. Britney that fucking prep started to cry. Vampire and Draco stopped fighting\ldots I shopped eating\ldots Everyone gasped. Da room fell silent\dotfill\newline\phantom{}\dotfill Volzemort!

\enquote{Eboby\dotfill Ebony\dotfill} Darth Valer sed evilly in his raspy voice. \enquote{Thou havfe failed ur mission. Now I shall kill thou and I shall kill Vampire as well. If thou does not kill him before then I shall kill Draco too!}

\enquote{Plz don't make me kill him plz!} I begged.

\enquote{No!} he laughed crudely. \enquote{Kill him, or I shall kill him anyway!} Then he flew away cackling.

I bust into tears. Draco and Vampire came to contort me. Suddenly my eyes rolled up so they looked all cool and gothic. I had a vision were I saw some lighting flash and then Voldremot coming to kill Draco while Draco slit his wrists in a depressed way.

\enquote{No!} I screamed sexily. Suddenly I locked up and stopped having the vision.

\enquote{Ebony Ebony aure you alright?} asked Draco in a worried voice.

\enquote{Yeah yeah.} I said sadly as I got up.

\enquote{Everyfing's all right Enoby.} said Vampire all sensetive.

\enquote{No its not!} I shouted angrily. Tearz of blood went down my face. \enquote{OMFG what if I'm getting possessed like in Da Ring 2!}

\enquote{Its ok gurl.} said B'loody Mary. \enquote{Maybe u should ask Proffesor Sinister about what the visions mean though.}

\enquote{Ok bich.} I said sadly and den we went.

