% !TeX root = ../my_immortal.tex
\section[]{\protect\makeEndnote[Chapter 29]{}{ch29}{This chapter was published on the same day as \citetitle{ghost}.}}

\AN{sot das fok up!11 ur jus jelouz koz ur prepz so fok u!1111 raven u rok gurl fangz 4 da help MCR ROX 666!111111111111}

\XXX{XXXXXXXXXXXX666\Xfill}

\enquote{Oh my satan!1} we screamed as we jamped out of da coffin. Snap and Professor McGoonagle started to shoot at us angrily.

\enquote{CUM NOW!1!} Preacher McGongel yielded. We did guiltily. We left the room putting on our clothes. Snoop garbed the caramel and put it in his pocket.

\enquote{Hey what the fuck!111} Vampire shooted angrily.

\enquote{Yeah buster what the fuck are u going to do with the fucking camera?} Draco demonded all protective, looking at me Longley with his gothic red eyes. \enquote{Look, Dumblehor noes your little secret and if u do dis again, then u will go to St Mango's. So give back da camera!1111}

Hahahaha the Mystery of Mogic thinks he is crazy there is no way dey wil believe him. Snoop laughed meanly.

\enquote{Yes so shut your mputh you inlosent fools!} yelled Proffesor McGoggle. She made us cum into a weird room with white stones all around it. There were all these werid tools in it. Draco started to cry all sexy and sexitive (\AN[]{geddit koz hes a sexbom lol \makeEndnote{tom felnot}{tom_felton}{English actor Tom Felton portrayed Draco Malfoy in the \citetitle{HP} film series.} rulez 4 lif but nut as muxh as gerard ur sex on legz I luv u u fokeng rok mary me!111}).

I started to cry tearz of blood (\AN[]{it hapnz in \makeEndnote{vrampir kroniklz}{vampire_chronicles}{\citetitle{vampire_chronicles} is a book series by American author Anne Rice, starting publication in 1976. The series pioneered depictions of vampires as erotic and emotional, crying tears of blood.} raven sed so ok so fok u!1}). Vampire took out a black honkerchief and started to wipe my red eyes.

And then\dotfill\newline he and Snoop both took out guns using magic. They started to shoot each other angrily. Non of the ballots gut on eachodder yet. I took out my wand.

\enquote{Crosio!} I shouted. Snap stated 2 scram he dropd da gun. But it was too late. Both of them had run out of ballets. I STOPPED DA CURSE\@. Profesor McGoogle did a spell so that we were all chained up. She took out a box of tools. Den she said \enquote{OK Serverus I'm going 2 go now.} She left. Snap started to laugh evilly. Vampire started to cry.

\enquote{It's ok Enoby.} said Draco. \enquote{Evergreen will be all right. Remember the cideo u took of Snake.}

Snape laughed again. And then\dotfill\newline he took out some whips!1!1111
