\stepcounter{section}
\section{\chaptername~\thesection}

\AN{I sed shut up itz nut my folt ok if u don't lik da story den ur a prep so fuk u flamerz\@!111\@1 ps im nut updating ubtil u giv me fiv god reviewz nd diz tim I men it!111111 U SUK\@!111\@1 fangz raven 4 di help il promiz to help u wif ur story lolz1}

\XXX{\Xfill 666\Xfill}

\enquote{Oh my fuking god!1} I shooted sadly. \enquote{Shud we get u 2 St Manga's, bitch?}

\enquote{Hel no!} she said. \enquote{Lizzen Egogy, I need ur help. Nex tim u go bak in tim, do u fink u kod ask Tom Andorson 4 sum help?}

\enquote{Sure I said sadly. I went outside the door. Draco was there!111 He wuz wearing a big blak GC tshit which wuz his panamas.}

\enquote{Hey Sexxy.} I said.

\enquote{How'd it go Enoby?} he asked in his voice was so sexy and low kinda like Gerard Way when hes talking.

\enquote{Fine.} I reponded. We stared 2 go bak in2 da dorm.

\enquote{How far did u go wif Satan?} Drako asked jealously.

\enquote{Not 2 far, lol.} I borked.

\enquote{Will you hav to do it with him?} Draco asked angstily.

\enquote{I hop not 2 far!111}\@ I shouted angrily. Den I felt bad 4 shooting at him. I said sorry. We frenched.

\enquote{What happened 2 Snipe?} I growled.

\enquote{U will see.} Draco giggled mistressly. He opened a door\dotfill\newline\phantom{}\dotfill Snap nd Lumpkin werz there!11 Serious waz pokering dem by staging dem wif a blak nife.

\enquote{NOOOO PLZ!1111} Lumpkin bagged as Serious started 2 suk his blood. I laffed statistically. I tok some photons of him and Snap bing torqued. (ok I no dis iz men but fink abot it ppl dey r pedoz nd Snap trid 2 rap dem and neway sadiztz rok haz any1 seen shrak atak 3 lolz). We took sum of Snipe's blod den Drako and I went bak 2 our roomz. We sat on my goffik blak coffin. My cloves were kinda drity so I pot on a blak leather outfit fingie kinda like da 1 Suelene haz in Undreworld. (if u haven't herd of it den FUK U!111) . I put on some blak platform high heelz. Darko put on `desolition liverz' by MCR. Den\dotfill\newline
we storted 2 take of eachotherz clozez. I tok of his shit nd he had a six-pak, lolz. We started 2 mak out lik in Da Grudge. He pot his wetnes in my u-know-what sexily. I gut an orgy.

\begin{sloppypar}
    \enquote{Oh Draco!111111!\@1 Oh mi fuking gud Draco!1111} I screemed passively as he got an eructation.
\end{sloppypar}

\enquote{I luv u TaEbory.} he whispred sexily and den we fel aspleep lol.
