\stepcounter{section}
\section{\chaptername~\thesection. I Am A Trolling Genious, lolz}

\AN[Disclaimer: ]{I do not own the HP series and I am not the real XXXbloodyrists666XXX.}

\AN[\textbf{AN}// ]{I am an extremely immature pathetic idiot girl, I know. Out of boredom, I crack this girl's passy for fun (and it took less than 8 minutes to do it too) and will probably get in a shitload of trouble. Which I probably deserve `cause I'm being a troll right now. Meh.

And I present to you MY crappy part in this story. (And take note I haven't even finished reading this fic yet, but instead skip over to skim chapter 38.) Flame, laugh, do whatever you want \enquote{preps.}}

I, the American retail wearing british vampire Sue, coughed up blood.

Satan kneeled down beside me.

\enquote{Noooooooooooooooo! Don't die!}

I gave him a rueful smile. \enquote{I'm sorry. It's something I had to do, to fufill my duty as the noble gothic Mary Sue.}

Satan sobbed. \enquote{I love you Ebony.}

\enquote{I love you two. I'll\ldots I'll see you in hell.} I mumbled, already finding my surroundings fading to black.

B'loody Mary Smith suddenly popped into the room for no apparent reason. She frowned when she realized the room was oddly quiet, but at the sight of Ebony's lifeless body, she screamed. Her face became pale with horror. She screamed for the healers, Dumbledore, Mcgoogle, and every single gothic person she could think of.

Suddenly, a glow started to surround the body of Ebony. Everyone stared in shock. Her body started to lift ever so slowly and then, to everyone's shock, it started to incinerate.

When everyone realized what was happening, they rushed over to try to rescue the body, but it was too late, the Sue became nothing more then a pile of ashes.

A loud resounding of everyone bellowing \enquote{NOOO\-O\-O\-O\-O\-O\-O\-O\-O\-O\-O\-O\-O\-O\-OOOOO\ldots!!} filled the room.

A flash of white light from the ashes then started to bounce around the room. Everyone cowered in fear and were temporarily blinded. When it was all over, things changed.

All the silly goth clothes dropped from everyone's bodies (\AN[\textbf{AN}//]{I will refuse to explain how the hell that happened.}) and, in their place, clothes the characters would normally wear in canon appeared on their bodies.

\begin{sloppypar}
    When everyone got over the shock of becoming free of the gofick power, everybody cheered. Everyone started singing \enquote*{Ding dong the sue is dead\ldots} Well, that is, until all the HP characters realized the true implications of becoming more canon like again.
\end{sloppypar}

All the characters who were supposed to be dead fell to the floor, their bodies cold and lifeless. Harry and Voldemort started dueling. On the left side of the two, the battle of the Light Side and the Dark Side were reaching a climax.

And, because the replacement author also likes to screw around with canon, Draco and Hermione fled the scene and got married.

\rule{1in}{0.4pt}

Meanwhile\ldots

Down in hell, Ebony shed a single tear because of her current situation. A situation that would live on for all eternity. Or at least until the end of fanfiction time.

She lost it all, but she knew she had to remain strong. Nothing would ever break her down.

She looked down over her pale body, and frowned. \enquote*{Where are my emo clothes?} She asked herself in confusion.

And then it occured to her\ldots

For her shirt, she was wearing a bright pink polo with a little seagull on the (right or left? I can't remember) side. Below that, she was wearing a denim miniskirt with the \enquote{destroyed} look on it. Paired underneath that skirt were leggings with a little moose at the bottom. And then Ebony realized, on her shoulder, she was carrying a pretty bag with an eagle on it that said Live Your Life written all over the bag.

Ebony supressed the urge to scream. Here she was decked out in clothes prep to the extreme wearing stuff from Abercrombie and Fitch, American Eagle, AND Hollister.

\begin{sloppypar}
    Panicked, Ebony hastily tried to take off the Hollister polo, but underneath it, there was another Hollister polo underneath. Ebony frowned, and looked under her shirt. All she saw was a bra underneath (dare I point out it's from the Aerie line available at American Eagle?). Ebony tried to remove the shirt again. But to her frustration, there was yet again another polo to replace it.
\end{sloppypar}

\begin{sloppypar}
    T\enquote{HIS IS UNLOGICAL AND DOES NOT MAKE ANY SENSE!!} Ebony bellowed out to the air. She failed to see the irony in her statement, how hypocrytical her words were, seeing as she was practically calling the kettle black here.
\end{sloppypar}

Ebony slit her writs and mumbled to herself, \enquote{Omigod.}

\AN[]{/End Crap Fic.}

\vspace{1em}

\AN[\textbf{AN}// ]{Oh yeah, if you wanna see the original content this chick had planned for this chapter, I accessed it through the document manager thingy, which I copied and pasted, so you can read it here:}

\AN{stfu prepz git a lif!111111 U SUCK!11 oh and form now on il be in vocation in englind until lik august so I wont be able 2 update 4 a while, lolz. fangz 2 evry1 hu revoiwed expect da prepz hu flamed FOK U!1 MCR RULEZ 666!111}

\XXX{\Xfill XXXXX666\Xfill}

I woke up in da Norse's offace on a special gothik coffin. Hairgrid wuz in da bed opposite me in a comma coz Vampir and Draco had bet him up. Mr.~Noris was cleaning the room.

\enquote{Oh mi satan wut happened!} I screamed. Suddenly Volxemort came. He loked less mean then usual.

\enquote{Get the fuk out u fucking bastard!11} I yielded.

\enquote{Thou hath nut killd Vampire yet!11} he said arngrily. Sudenly he started 2 cry tearz of blood al selective.

\enquote{Volxemort? OMFG what's wrong!111} I asked.

Sudenly\dotfill Lucian, Profesor Sinister and Serious came!\newline B'lody Mary and Vampire were wif dem. Every1 was holding blak boxez. VOLXEMORT DISAPAERD\@.

\enquote{OMFG Enoby ur alive!111} Scremed Vampire. I hugged him and B'lody Mary.

\enquote{What the fuk happened?} I asked dem. \enquote{Oh my satan!11 Am I lik dead now?} I gosped.

\enquote{Enoby u were almost shot!11} said Serious. \enquote{But da ballet could not kill u since u were form anodder time.}

\enquote{But fangz anyway!1} said Lucian holding oot his arm. I gasped. He had two arms!

\enquote{OMG I cant beleve Vampirz' dad shot u!1} I gasped.

\enquote{Well 2 be honest Snap wuz pozzesd by Snap bak den.} said James.

\enquote{Yah he wuz a spy.} Serious said sadly. \enquote{He wuz really a Death Dealer.}

\enquote{And he wuz such a fuking poser 2!11} said Lucian. \enquote{He didn't even realy no hu GC were until I told him.} Well anyway everyone tarted 2 give me presents. I was opening a blak box wif red 666s (there wuz a dvd of corps bride in it) on it when I gasped. Mr. Noris looked up angrily coz he h8ed gothz.

\enquote{Hey haz aneone fuking seen Draco?} I asked gothikally.

\enquote{No Draco told me he wood be watching Hoes of Wax.} said Profesor Trevolry. \enquote{He duzzn't know dat ur better. Anyway da norse said u could get up. Cum on!1}

I got up suicidally. Lucian, Serious and Profesor Sinister left. I wuz wearing a blak leather nightgun. Under that I had on a sexxy blak leather bra trimed wif blak lace, with a matching thong that said goffik gurl on the butt and sexy fishnetz that kind hooked on 2 my thong (if u don't get da idea massage me ill tell u). I put on a blak fishnet top under a blak MCR t-shirt, a blak leather mini with blak lace and congress shoes. I left the hospital's wings wif B'lody Mary, Willow and Vampire.

\enquote{OMFG letz celebrate!11} gasped Willow.

\enquote{We can go c Hose of Wax wif Draco!1} giggled Vampire.

\enquote{Letz go lizzen 2 GC and kut ourselvz 666!11} said Hermoine. We opened da conmen room door sexily. And den\dotfill\newline I gasped\dotfill Draco wuz there\newline doing it wif Snap!1111111111111111111111111 He wuz wearing a blak tshirt wif 666 on da front and baggy jeanz.

\enquote{U fucking prep!11} we all yielded angrily.

\enquote{Yah u betrayed us!111} shooted Vampire angrily as he took out his blak gun.

\enquote{No u don't understand!1} screamed Draco sadly as he took his thingie out of Snake's.

\enquote{No shit u fuking suk u preppy bastard!111} said Willow trying 2 attak him (u rok girl!1). I ran suicidally to my room I sexily took a steak out.

\enquote{Enoby no!11111} screamed Draco but it wuz 2 l8 I had slit muh ritsts wif it suddenly everyfing went blak again.

\par\nobreak\vspace{1em}\noindent
\rule{1in}{0.4pt}

\begin{sloppypar}
    \noindent\AN[]{Sincerely,\\
        An-Anon-Author-Who-Will-Silently-Not-Reveal-Her-Identity-Because-She's-A-Coward :P\\
        A.K.A. Just a troll with rocks for brains.}
\end{sloppypar}