\section{}

\AN{stop flaming ok! I dntn red all da boox! dis is frum da movie ok so itz nut my folt if dumbeldor swers! besuizds I SED HE HAD A HEDACHE\@! and da reson snap dosent lik harry now is coz hes christian and vampire is a satanist! MCR ROX\@!}

\XXX{XXXXXXXXXXXXXXXXXX666\Xfill}

I was so mad and sad. I couldn't believe Draco for cheating on me. I began to cry against the tree where I did it with Draco.

Then all of a suddenly, an horrible man with red eyes and no nose and everything started flying towards me on a broomstick! He didn't have a nose (basically like Voldemort in the movie) and he was wearing all black but it was obvious he wasn't gothic. It was\dotfill Voldemort!

\enquote{No!} I shouted in a scared voice but then Voldemort shouted \enquote{Imperius!} and I couldn't run away.

\enquote{Crookshanks!} I shouted at him. Voldemort fell of his broom and started to scream. I felt bad for him even though I'm a sadist so I stopped.

\enquote{Ebony.} he yelled. \enquote{Thou must kill Vampire Potter!}

I thought about Vampire and his sexah eyes and his gothic black hair and how his face looks just like Joel Madden. I remembered that Draco had said I didn't understand, so I thought, what if Draco went out with Vampire before I went out with him and they broke up?

\enquote{No, Voldemort!} I shouted back.

Voldemort gave me a gun. \enquote{No! Please!} I begged.

\enquote{Thou must!} he yelled. \enquote{If thou does not, then I shall kill thy beloved Draco!}

\enquote{How did you know?} I asked in a surprised way.

Voldemort got a dude-ur-so-retarded look on his face. \enquote{I hath telekinesis.} he answered cruelly. \enquote{And if you doth not kill Vampire, then thou know what will happen to Draco!} he shouted. Then he flew away angrily on his broomstick.

I was so scared and mad I didn't know what to do. Suddenly Draco came into the woods.

\enquote{Draco!} I said. \enquote{Hi!}

\enquote{Hi.} he said back but his face was all sad. He was wearing white foundation and messy eyeliner kind of like a pentagram (geddit) between Joel Madden and Gerard Way.

\enquote{Are you okay?} I asked.

\enquote{No.} he answered.

\enquote{I'm sorry I got all mad at you but I thought you cheated on me.} I expelled.

\enquote{That's okay.} he said all depressed and we went back into Hogwarts together making out.
