% !TeX root = ../my_immortal.tex
\section{}

\AN{fuk u ok! u fokng suk. itz nut ma fult if itz speld rong ok koz dat bich ravern cuz it fok u prepz!1 woopz soz raven fangz 4 da help. btw transilvana rox hrad!1 I even gut 2 go 2 da kasel wer drkola was flimed!}

\XXX{\Xfill 666XXXXXXXXXXXXXXX}

Later we all went in the skull. Draco was crying in da common room. \enquote{Draco are u okay?} I asked in a gothic voice.

\enquote{No I'm not u fuking bitch!} he shouted angrily. He stated to run out of the place in a suicidal way. I stated to cry cuz I was afraid he would commit suicide.

\enquote{Its ok Enoby.} said Vampire comfortly. \enquote{Ill make him feel better.}

\enquote{U mean you'll go fuck him wont you!} I shouted angrily. Then I ran 2 get Draco. Vampire came too.

\enquote{Draco please come!} he began to cry. Tears of blood came down his pail face. I wuz so turned on cuz I love sensitive bi guyz. (if ur a homophone den fuk of!)

And then\dotfill we herd sum footsteps! Vampire got out his blak invincibility coke. We both gut under it. We saw the janitor Mr. Norris there, shouting angrily with a flashlight in his hand.

\enquote{WHOSE THERE\@!} he shouted angrily. We saw Filth come. He went unda da invisibility cloke and started to meow loudly.

\enquote{IS ANY1 THERE\@!} yelled Mr.~Norris.

\enquote{No fuck u you preppy little poser sun of a fukcing bich!} Vampire said under his breast in a disgusted way.

\enquote{EXCUS ME\@! EXCUS ME WHO SED DAT\@!} yelled Mr. Norris. Den he heard Filch meow. \enquote{Filth is der any1 unda da cloak!} he asked. Filth nodded. And then\dotfill\newline Vampir frenched me! He did it jus as\dotfill\newline Mr.~Norris was taking of da cloak!1

\enquote{WHAT DA-} he yelled but it was 2 late cuz now we were ruining away frum him. And den we saw Draco crying n bustin in2 tearz and slitting his rists outside of da school.

\enquote{Draco!} I cried. \enquote{R u okay?}

\enquote{I guess though.} Draco weeped. We went back to our coffins frenching each other. Draco and I decided to watch Lake Placid (c isnt da deprezzin) on the gothic red bed together. As I wuz about 2 put in the video, my eyes rolled up and suddenly I had a vision of something that was happening now. There was a knok on the door and Fug and da Mystery of Magic walked into the school!1

