\section{}

\AN{I sed I dnoty ker wut u fink! stof pflamin ok prepz!1 fangz 2 raven 4 da help!1 oh yah btw ill be un vacation in transilvania 4 da nex 3 dayz so dnot expect updatz.}

\XXX{\Xfill 666XXXXXXXXXXXXXXX}

All day I wondered what the surprise was. Meanwhile, I pot on a blak ledder mini, a blak corset with urple lace stuff all over it, an black gothic compact boots. MCR were gong 2 do the concert again, since Volxemort had taken over the last one. I slit my wrists while I moshed 2 MCR in my bedroom all night, feeling excited. Suddenly someone knocked on the door while I was trying on sum black clothes and moshing to Fang u 4 da Venom. I gut all mad and turned it of, but sacredly I hopped inside dat it was Draco so we could do it again.

\enquote{Wut de fucking hell r u doing!} I shouted angrily. It was Loopin! \enquote{R u gonna cum rape me or what.} I yelled. I was allowed to say dat because Dumblydore had told us all 2 be careful around hem and Snap since he was a pedo.

\enquote{No, actshelly (geddit, hell) kan I plz burrow sum condemns.} he growld angrily.

\enquote{Yah, so u can fuk ur six-yr-old gurlfriend, huh?} I shouted sarkastikally.

\enquote{Fuker.} He said, gong away.

Well anyway, I put on some black eyesharow, black eyeliner, and some black lipstick and white foundation. Then I went. Den I gasped\dotfill\newline Snake and Loopin were in da middle of da empty hall, doin it, and Dobby was watching!1

\enquote{Oh my god you ludacris idiot!} they both shooted angrily when they saw me. Dobby ran away crying. Dey got up, though. Normally I wood have ben turned on (I luv cing guyz do it) but both of them were fuking preps. (btw snake is movd 2 griffindoor now)

\enquote{WTF is that why u wanted condoms?} I asked sadistically. (c I speld dat)

\enquote{Only you wouldn't give them to me!} Lumpkin shouted angrily.

\enquote{Well you shoulda told me.} I replayed.

\enquote{You dimwit!.} Snake began 2 shoot angrily. And then\dotfill I took out my black camera and took a pic of them. U could see that they were naked and everything.

\enquote{Well xcuse me!} they both shouted angrily. \enquote{What was dat al about?}

\enquote{It wuz to blackmail u.} I snarked. \enquote{So now next time you see me doing it with my boyfriend you cant fuking rat me out or I'll show dis to Dumbledork. So fuck off, u bastards!} I started to run. They chased me but I threw my wound at them and dey tripped over it. Well anyway, I went outside and there was Vampire, looking extremely fucking hot.

\enquote{WTF where'd Draco?} I asked him.

\enquote{Oh he's bein a fucking bastard. He told me he wouldn't cum.} Vampire said shaking his hed. \enquote{U wanna cum with me? 2 the concert?}

Then\ldots\ldots he showed me his flying car. I gasped. It was a black car. He said his dogfather Serious Blak had given it 2 him. The license plate on the front sed MCR666 on it. The one on da back said \enquote*{ENOBY} on it.

\ldots\ldots I gasped.

We flew to the concert hall. MCR were there, playing.

Vampire and I began 2 make out, moshing to the muzik. I gapsed, looking at da band.

I almost had an orgasim. Gerard was so fucking hot! He begin 2 sing \enquote*{Helena} and his sexah beautiful voice began 2 fill the hall. \ldots\ldots And den, I heard some crrying. I turned and saw Draco, cryin in a corner.

