% !TeX root = ../my_immortal.tex
\section{}

\AN{wut doez every1 fink if I end da strory and den I add sum more 2 it after vocation? oh yah asnd prepz stup flaming if u dnot lik dat story den take muh quiz ok den u wil c if ur gofik or not!1111111}

\XXX{\Xfill 6666XXX\Xfill}

Satan and I walked 2 his car. It wuz a blak car wif pentagrams all over it. On da license plate said 666 just lik Draco's car. I went in it seduktivly. Stan started 2 drive it. We talked about Satanism (lolz he wuz named after Satan), kuttting, musik and being goffik.

\enquote{Oh my satan, Gerard is so fuking hot!11} Volxemort agreed as we smoked sum weed. (koz bi guyz r hot dey r so sensitive I luv dem lol goez fux a bi guy)

\enquote{Lol, I totally decided not 2 comit suicide when I herd Hilena.} I said in a flirty voice. \enquote{\dotfill Hey Satan do u know da cure 4\newline when ppl r adikted 2 Volxemortseruem?}

\enquote{Well\dotfill} he thought. \enquote{I fink u have 2 drink Vampire blod.}

Suddenly Volxemort parked da car behind a blak movie theater. Satan and I walked outside. We went in2 da movie tether were they were showing da Excercist. In it a boy and a gurl were doing it sudenly a cereal killer came lol. Satan and I laughed at da blood koz we're sadists.

While Satan was watching da movie, I had an idea. I took Satan's gothic blak Nightmare b4 Christmas cigar sexily from his poket and put sum Amnesia potion in it. I put it bak in his blak Emile the Strange bag. Satan turned arund and started 2 smoke it. Blak cloudz wif red pentagramz ind em started 2 fly around everywhere.

\enquote{OMG!111} Satan said jumping up. I gasped koz I wuz afraid hed notizd. \enquote{Enoby gess what?}

I new that the amnesia had worked.

\enquote{Amnesia potion has not been invented yet so it will not work.} He said. \enquote{2 badd coz I wanted 2 use sum on u.}

\enquote{Kul.} I raised my eye suggestingly. And den\dotfill\newline
he tok of my cloves sexily and we started 2 make out. I tok of his shit. He had six-pak justr lik Gerard Way!11 We frenched.

\enquote{Xcuze me but u r going 2 have 2 leave!111} shooted da lady behind us she was a prep.

\enquote{Fuk u!11} I said. Suddenly\dotfill\newline I attaked her suking all her blood.

\begin{sloppypar}
    \enquote{Noooooo!11} she screamed. All the preps in da theater screamed but everyone else crapped koz Satan and I loked so cute 2gether. Satan and I started to walk outside.    
\end{sloppypar}

\enquote{Zomg how did u do that?} Voldremort asked in a turned-on voice.

\enquote{I'm a vampire.} I said as we went into the car.

\enquote{Siriusly?} he gasped.

\enquote{Yah siriusly.} I said drinking sum beer. Satan started 2 drive da car. I smelled happily.

\enquote{Itz too bad we didn't get 2 c da rest of the movie, don't u fink?}

\enquote{Yah.} I said as we kised passively. Satan parked in a blak driveway next 2 da place where Draco and I had watched GC for the frist time. We went inside where Marylin Mason wuz playing and started to mosh lol.

\begin{sloppypar}
    \enquote{Anti-ppl now uve gone 2 far Jeus Krist Superstar!1111} screamed Marlin on da stage. We did the devil fingers. I started 2 dance really close to Satan. He was so shmexay!1 He looked at me all emo with his gothic red eyes and he looked exactly like Mikey Way. I almost got an orgaism!1 Suddenly Marylin Mason stopped singing.    
\end{sloppypar}

\enquote{I wood like to peasant\dotfill XBlakXTearX!11} he said.\newline I ran onstage. Lucian, Samaro, Snap and Hades were there. They started 2 play their instilments. I got onstag.

\enquote{Wel if u wonted honesty datz all u had 2 say!1111} I sang. (I dnot own da lyerix 2 dat song) My voice sounded lik a pentagram betwen Amy Lee and a gurl version of Gerard Woy. Everyone clappd. Satan got an eructation. \enquote{I'M NUT OKAY!1} I sang finaly. Suddenly Lucian started playing da song wrong by mistak.

\enquote{OMFG!1} yielded James. \enquote{Wut the fuck?}

\enquote{Woops im sory!} said Lucian.

\enquote{You fuking ashhole!1} James shouted angrily.

\enquote{U guys are such prepz!11} Snap said. \enquote{Cum on it wuz a mistake!1}

\enquote{Yah itz not his fault!11} said Serious.

\enquote{No he ruined the fucking song!1} yelled Samaro.

\enquote{U guys stop!11} I shotoed angrily but it waz 2 late. They all began 2 fight. Sudenly Samaro took out hiz nife.

\enquote{OMFG no!11} shouted Lucan but it wuz 2 late James tried 2 shoot off his arm.

And den\dotfill I jumped secxily in front of da bullet!11

\enquote{No!111} yielded everyone but it wuz 2 late suddenly everyfing went blak.
