% !TeX root = ../my_immortal.tex
\cleardoublepage\chapter{Fanfiction.net User Profiles}

\section{XXXbloodyrists666XXX}
\DTMsavedate{regdate_Tara}{2006-03-01}
\DTMsavedate{profile_Tara}{2009-12-21}
\begin{description}
	\item[Joined] \DTMusedate{regdate_Tara}
	\item[Updated] \DTMusedate{profile_Tara}
	\item[URL] \href{https://www.fanfiction.net/u/999831/XXXbloodyrists666XXX}{\texttt{fanfiction.net/u/999831/XXXbloodyrists666XXX}}
\end{description}

EVRY1 C NEW MOON!!1 i will try 2 post a new fanfik
maybe derring da summer but i probebly wont koz all
od u r such idiotz. u hakked mi account and u flamed
mi story. fuk da world!!1 fuk all of u bichez!!1

Im Tara. Im a Stanistr and if u dont lik me cos of
dat den FUK OFF!. if ur a prep or a pozr den fuk off
2 koz ur gay!! here r sum fingz u shud no abot me.

likez: gothz, being goffik, satan, punkz, da coler
black, bloood, ma bf Justin, rok muzik, suicide,
vampires, joel madden, edard kullen!!

dislikez: prepz, posers, pink, being alive,
homophobez, skool, life, barbie, flamerz

Fave muzik: GC, MCR, Evinezenz, Linin prak, BLINK183,
mraliyn manson, panik at da desko, goofik bandz, paramor!!1

\begin{sloppypar}
	lest faveorite musik: ASHLEEE SIMPSON britney spearz,
	hilery duff, linzee lohan ALL POP
\end{sloppypar}

\begin{sloppypar}
	Fav movies: cropse bride, mean gurlz, van helsing, any
	odder horror moviw, nightmare b4 christmas, da ring,
	da ring 2, da grudg 2, saw2 and saw 3, da omen, scary movie 4,
	cursed, TWILITE, NEW MOON
\end{sloppypar}

if ur not a gottik den fuk u!!

\section{bloodytearz666}
\DTMsavedate{regdate_Raven}{2005-09-26}
% \DTMsavedate{profile_Raven}{}
\begin{description}
	\item[Joined] \DTMusedate{regdate_Raven}
	\item[Updated] \textit{Never} %\DTMusedate{profile_Raven}
	\item[URL] \href{https://www.fanfiction.net/u/903576/bloodytearz666}{\texttt{fanfiction.net/u/903576/bloodytearz666}}
\end{description}

Hi, I'm Raven. That's not my real name but my real name (Jennie) is crappy
so don't call me that. I am 14 years old. I'm a WS, which means a wrist-slitter.
In fact, a close friend of mine recently commited suicide by doing that,
but I don't want2 talk about it. My favorite movies r The Grudge, Underworld,
Shark Attack 2, The Ring, Corpse Bride and the Nightmare before Christmas.
(There's more (mostly horror and stuff even tho they don't scare me)but I don't
feel like lisitinf it). I HATE comedies. The world is so shitty, why pretend it's not.
My favorite bands r My Chemical Romance, Evanescence, Simple Plan, Slipknot,
Marilyn Manson and Korn. I hate pop, music, preps and generally life.
I write stories about depression and that stuff mostly.

BTW check out my friend XXXbloodywrists666XXX's fanfic 2- it fucking rox.
